### 2016-09-30 gruntz.tex
Grammar, and use \eqref

Next, an arbitrary item $\omega$ is taken from mrv set that converges to zero for
$x\to\infty$ and doesn't have subexpressions in the given mrv set.  If such a term is not
present in the mrv set (i.e., all terms converge to infinity instead of zero),
the relation $f(x)\sim {1\over f(x)}$ can be used.  In the
considered case, only item $\omega=e^{-x}$ can be accepted.

The next step is to rewrite the mrv set in terms of $\omega=g(x)$.  Every element
$f(x)$ of the mrv set is rewritten as $A \omega^c$, where
\begin{equation}
\label{gruntz_rewrite}
c = \lim\limits_{x\to\infty} \frac{\log{f(x)}}{\log{g(x)}},
\qquad
A = e^{\log f - c \log g}
\end{equation}
Note that this step includes calculation of more simple limits, for instance
\begin{equation}
	\lim\limits_{x\to\infty} \frac{\log{e^{x + 2 e^{-x}}}}{\log e^{-x}}=
	\lim\limits_{x\to\infty} \frac{x + 2 e^{-x}}{-x} = -1
\end{equation}
In this example we obtain the rewritten mrv set: $\{{1\over\omega},
\omega, {1\over\omega}e^{2\omega}\}$. This can be done in SymPy with
\begin{verbatim}
>>> from sympy.series.gruntz import mrv, rewrite
>>> m = mrv(exp(x+2*exp(-x))-exp(x) + 1/x, x)
>>> w = Symbol('w')
>>> rewrite(m[1], m[0], x, w)[0]
1/x + exp(2*w)/w - 1/w
\end{verbatim}
Then the rewritten subexpressions are
substituted back into $f(x)$ in~(\ref{gruntz_example_fn})
and the result is expanded with respect to~$\omega$:
\begin{equation}
    \label{gruntz_example_fn2}
f(x) = {1\over x}-{1\over\omega}+{1\over\omega}e^{2\omega}
     = 2+{1\over x} + 2\omega + O(\omega^2)
\end{equation}

@@

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:\footnote{\label{suppnote:gruntz}To see the intermediate steps, discussed above, interested
readers can switch on debugging output by setting
the environment variable \texttt{SYMPY\_DEBUG=True}, before importing anything from
the SymPy namespace.}

@@

In general, when $f(x)$ is expanded in terms of $\omega$, the following is obtained:
\begin{equation}
f(x) = \underbrace{O\left({1\over \omega^3}\right)}_\infty
    + \underbrace{C_{-2}(x)\over \omega^2}_\infty
    + \underbrace{C_{-1}(x)\over \omega}_\infty
    + {C_{0}(x)}
    + \underbrace{C_{1}(x)\omega}_0
    + \underbrace{O(\omega^2)}_0
\end{equation}
The positive powers of $\omega$ are zero. If there are any negative powers of
$\omega$, then the result of the limit is infinity, otherwise the limit is
equal to $\lim\limits_{x\to\infty} C_0(x)$. The expression $C_0(x)$ is always
simpler than original $f(x)$, same is true for limits, arising in the
rewrite stage~(\ref{gruntz_rewrite}), so the algorithm converges. A proof of this and further
details on the algorithm are given in Gruntz's PhD thesis~\cite{Gruntz1996limits}.

>>>>

Next, an arbitrary item $\omega$ is taken from mrv set that converges to zero for
$x\to\infty$ and doesn't have subexpressions in the given mrv set.  If such a term is not
present in the mrv set (i.e., all terms converge to infinity instead of zero),
the relation $f(x)\sim {1\over f(x)}$ can be used.  In the
considered case, only the item $\omega=e^{-x}$ can be accepted.

The next step is to rewrite the mrv set in terms of $\omega=g(x)$.  Every element
$f(x)$ of the mrv set is rewritten as $A \omega^c$, where
\begin{equation}
\label{gruntz_rewrite}
c = \lim\limits_{x\to\infty} \frac{\log{f(x)}}{\log{g(x)}},
\qquad
A = e^{\log f - c \log g}
\end{equation}
Note that this step includes calculation of more simple limits, for instance
\begin{equation}
	\lim\limits_{x\to\infty} \frac{\log{e^{x + 2 e^{-x}}}}{\log e^{-x}}=
	\lim\limits_{x\to\infty} \frac{x + 2 e^{-x}}{-x} = -1
\end{equation}
In this example we obtain the rewritten mrv set: $\{{1\over\omega},
\omega, {1\over\omega}e^{2\omega}\}$. This can be done in SymPy with
\begin{verbatim}
>>> from sympy.series.gruntz import mrv, rewrite
>>> m = mrv(exp(x+2*exp(-x))-exp(x) + 1/x, x)
>>> w = Symbol('w')
>>> rewrite(m[1], m[0], x, w)[0]
1/x + exp(2*w)/w - 1/w
\end{verbatim}
Then the rewritten subexpressions are
substituted back into $f(x)$ in~\eqref{gruntz_example_fn}
and the result is expanded with respect to~$\omega$:
\begin{equation}
    \label{gruntz_example_fn2}
f(x) = {1\over x}-{1\over\omega}+{1\over\omega}e^{2\omega}
     = 2+{1\over x} + 2\omega + O(\omega^2)
\end{equation}

@@

In this example the result ($2+{1\over x}$) still depends on $x$, so the above procedure is
repeated until just a value independent of $x$ is obtained. This is the final
limit. In the above case the limit is $2$, as can be
verified by SymPy:\footnote{\label{suppnote:gruntz}To see the intermediate steps discussed above, interested
readers can switch on debugging output by setting
the environment variable \texttt{SYMPY\_DEBUG=True}, before importing anything from
the SymPy namespace.}

@@

In general, when $f(x)$ is expanded in terms of $\omega$, the following is obtained:
\begin{equation}
f(x) = \underbrace{O\left({1\over \omega^3}\right)}_\infty
    + \underbrace{C_{-2}(x)\over \omega^2}_\infty
    + \underbrace{C_{-1}(x)\over \omega}_\infty
    + {C_{0}(x)}
    + \underbrace{C_{1}(x)\omega}_0
    + \underbrace{O(\omega^2)}_0
\end{equation}
The positive powers of $\omega$ are zero. If there are any negative powers of
$\omega$, then the result of the limit is infinity, otherwise the limit is
equal to $\lim\limits_{x\to\infty} C_0(x)$. The expression $C_0(x)$ is always
simpler than original $f(x)$, and the same is true for limits arising in the
rewrite stage~\eqref{gruntz_rewrite}, so the algorithm converges. A proof of this and further
details on the algorithm are given in Gruntz's PhD thesis~\cite{Gruntz1996limits}.
